Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-14 write-ups/PLDI/paper.tex
Add expe set up on standalone vs skip task

>>>>

\paragraph{Experimental setup} \ADComment{Describe the data we are
  gathering.}  The introduction of cooperative scheduling primitives
introduces an overhead even if no killing, forking or resizing ever
happen. We measure this overhead by comparing execution times of the
original kernel and the cooperative one, forcing the scheduler to
never modify the number of active workgroups. Since the cooperative
kernel contains the non-persistent task code anyway, its occupancy
bound may be less than the original kernel; we make sure to use this
occupancy bound as the number of workgroups for the original kernel in
order to compare relevant execution times.
